Online Verification of Commutativity

### 2020-10-08 acmPaper/paper.tex
author info
replaces all but one of the pdfs, hacks to acm class
final pdf image
add pdf's
fixes

\newcount\draft\draft=0 % set to 0 for submission or publication
% \documentclass[sigplan,review,anonymous]{acmart}
% \documentclass[sigplan,nonacm=true]{acmart}
\documentclass[sigplan]{acmart}
\setcopyright{none}
%
\usepackage{tikz}
\usetikzlibrary{snakes}
\usepackage[norelsize]{algorithm2e}
\usepackage{xxx}
\usepackage{fncylab}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{microtype}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

\begin{CCSXML}
    <ccs2012>
       <concept>
           <concept_id>10003752.10003766.10003776</concept_id>
           <concept_desc>Theory of computation~Regular languages</concept_desc>
           <concept_significance>500</concept_significance>
           </concept>
       <concept>
           <concept_id>10003752.10003809.10003635.10010038</concept_id>
           <concept_desc>Theory of computation~Dynamic graph algorithms</concept_desc>
           <concept_significance>500</concept_significance>
           </concept>
     </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Theory of computation~Regular languages}
\ccsdesc[500]{Theory of computation~Dynamic graph algorithms}

@@

\begin{document}
\settopmatter{printacmref=false}
\title{Online Verification of Commutativity}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Aditi Kabra \quad Dietrich Geisler \quad Adrian Sampson}
\affiliation{%
  \institution{Cornell University}
}

@@

\begin{figure}
    % TODO format nicely.
    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_OptimalSet.png}
      \caption{~\ref{algo_online_minimal}}
      \label{fig:sfigOptimalTvsS}
    \end{subfigure}

    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_Polynomial.png}
      \caption{~\ref{algo_online_polynomial}}
      \label{fig:sfigPolynomialTvsS}
    \end{subfigure}

    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_NaiveChecker.png}
      \caption{Naive baseline}
      \label{fig:sfigNa\"{i}veTvsS}
    \end{subfigure}

@@

    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_TwoFlipPathChecker.png}
      \caption{Two flip tolerant baseline}
      \label{fig:sfigTwoFlipTvsS}
    \end{subfigure}

    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_BatchChecker.png}
      \caption{Batch algorithm baseline}
      \label{fig:sfigBatchTvsS}
    \end{subfigure}
    \caption{Plots of scaling of time with input size and density}
    \label{fig:timeVsSize}
\end{figure}

@@

\begin{figure}
    % TODO format nicely.
    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{variance_10_OptimalSet.png}
      \caption{~\ref{algo_online_minimal}}
      \label{fig:sfigOptimalSpread}
    \end{subfigure}

    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{variance_10_Polynomial.png}
      \caption{~\ref{algo_online_polynomial}}
      \label{fig:sfigPolynomialSpread}
    \end{subfigure}

    % \begin{subfigure}{\linewidth}
    %   \includegraphics[width=\linewidth]{variance_10_TwoFlip.png}
    %   \caption{Two flip tolerant baseline}
    %   \label{fig:sfigTwoFlipSpread}
    % \end{subfigure}

>>>>

\newcount\draft\draft=0 % set to 0 for submission or publication
% \documentclass[sigplan,review,anonymous]{acmart}
% \documentclass[sigplan,nonacm=true]{acmart}
\documentclass[sigplan]{acmart}
%

\usepackage{tikz}
\usetikzlibrary{snakes}
\usepackage[norelsize]{algorithm2e}
\usepackage{xxx}
\usepackage{fncylab}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{microtype}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

\begin{CCSXML}
    <ccs2012>
       <concept>
           <concept_id>10003752.10003809.10003635.10010038</concept_id>
           <concept_desc>Theory of computation~Dynamic graph algorithms</concept_desc>
           <concept_significance>500</concept_significance>
           </concept>
     </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Theory of computation~Dynamic graph algorithms}

@@

\begin{document}
\settopmatter{printacmref=true}
\title{Online Verification of Commutativity}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Aditi Kabra}
\affiliation{%
  \institution{Carnegie Mellon University}
  \city{Pittsburgh}
  \state{PA}
  \country{USA}
}
\email{akabra@cs.cmu.edu}

\author{Dietrich Geisler}
\affiliation{%
  \institution{Cornell University}
  \city{Ithaca}
  \state{NY}
  \country{USA}
}
\email{dag368@cornell.edu}

\author{Adrian Sampson}
\affiliation{%
  \institution{Cornell University}
  \city{Ithaca}
  \state{NY}
  \country{USA}
}
\email{asampson@cs.cornell.edu}

@@

\begin{figure}
    % TODO format nicely.
    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_OptimalSet.pdf}
      \caption{~\ref{algo_online_minimal}}
      \label{fig:sfigOptimalTvsS}
    \end{subfigure}

    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_Polynomial.pdf}
      \caption{~\ref{algo_online_polynomial}}
      \label{fig:sfigPolynomialTvsS}
    \end{subfigure}

    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_NaiveChecker.pdf}
      \caption{Naive baseline}
      \label{fig:sfigNa\"{i}veTvsS}
    \end{subfigure}

@@

    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_TwoFlipPathChecker.pdf}
      \caption{Two flip tolerant baseline}
      \label{fig:sfigTwoFlipTvsS}
    \end{subfigure}

    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{timeVsSize_10_BatchChecker.pdf}
      \caption{Batch algorithm baseline}
      \label{fig:sfigBatchTvsS}
    \end{subfigure}
    \caption{Plots of scaling of time with input size and density}
    \label{fig:timeVsSize}
\end{figure}

@@

\begin{figure}
    % TODO format nicely.
    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{variance_10_OptimalSet.pdf}
      \caption{~\ref{algo_online_minimal}}
      \label{fig:sfigOptimalSpread}
    \end{subfigure}

    \begin{subfigure}{\linewidth}
      \includegraphics[width=\linewidth]{variance_10_Polynomial.pdf}
      \caption{~\ref{algo_online_polynomial}}
      \label{fig:sfigPolynomialSpread}
    \end{subfigure}

    % \begin{subfigure}{\linewidth}
    %   \includegraphics[width=\linewidth]{variance_10_TwoFlip.pdf}
    %   \caption{Two flip tolerant baseline}
    %   \label{fig:sfigTwoFlipSpread}
    % \end{subfigure}
